Process_MCData

### 2024-04-02 Code/Process_MCData.Rmd
Lined up code so that they were easier to read

                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),

@@

                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),  Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm =  TRUE)))/max(.$time), Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),

@@

   mutate(GrowthAmpdeltaOD = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720)))

@@

#Growthamp flags to determine if growth occurred before 14 days 
ProcessDataNestGrowth2 <- ProcessDataNestGrowth %>%
  unnest(c(tubedata)) %>%
   filter(time <= GrowthAmpWindow) %>%
  nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720,
                  ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
   mutate(GrowthAmpdeltaOD_14days = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720_14days = if_else(OD720_TimetoMax <= MaxAmpHour| is.na(OD720_TimetoMax) , map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720))),
          minRollMeanOD720_14days = map(tubedata, ~min(.$rollmeanOD720, na.rm = TRUE)),
          maxRollMeanOD720_14days = map(tubedata, ~max(.$rollmeanOD720, na.rm = TRUE)),
          minRollMeandeltaOD_14days = map(tubedata, ~min(.$rollmeandeltaOD, na.rm = TRUE)),
          maxRollMeandeltaOD_14days = map(tubedata, ~max(.$rollmeandeltaOD, na.rm = TRUE)),
          minRollMeanOD720_14days = as.numeric(minRollMeanOD720_14days),
          maxRollMeanOD720_14days = as.numeric(maxRollMeanOD720_14days),
          minRollMeandeltaOD_14days = as.numeric(minRollMeandeltaOD_14days),
          maxRollMeandeltaOD_14days = as.numeric(maxRollMeandeltaOD_14days)
           )

>>>>

                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  
                                         Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time),
                                         Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),

@@

                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),
                                         Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm =  TRUE)))/max(.$time),
                                         Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),

@@

   mutate(GrowthAmpdeltaOD = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax),
                                     map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)),
                                     map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax),
                                   map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)),
                                   map(tubedata, ~growth_amp(y = .$rollmeanOD720)))

@@

#Growthamp flags to determine if growth occurred before 14 days 
ProcessDataNestGrowth2 <- ProcessDataNestGrowth %>%
  unnest(c(tubedata)) %>%
   filter(time <= GrowthAmpWindow) %>%
  nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720,
                  ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
   mutate(GrowthAmpdeltaOD_14days = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax),
                                            map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)),
                                            map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720_14days = if_else(OD720_TimetoMax <= MaxAmpHour| is.na(OD720_TimetoMax),
                                          map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)),
                                          map(tubedata, ~growth_amp(y = .$rollmeanOD720))),
          minRollMeanOD720_14days = map(tubedata, ~min(.$rollmeanOD720, na.rm = TRUE)),
          maxRollMeanOD720_14days = map(tubedata, ~max(.$rollmeanOD720, na.rm = TRUE)),
          minRollMeandeltaOD_14days = map(tubedata, ~min(.$rollmeandeltaOD, na.rm = TRUE)),
          maxRollMeandeltaOD_14days = map(tubedata, ~max(.$rollmeandeltaOD, na.rm = TRUE)),
          minRollMeanOD720_14days = as.numeric(minRollMeanOD720_14days),
          maxRollMeanOD720_14days = as.numeric(maxRollMeanOD720_14days),
          minRollMeandeltaOD_14days = as.numeric(minRollMeandeltaOD_14days),
          maxRollMeandeltaOD_14days = as.numeric(maxRollMeandeltaOD_14days)
           )
